### 2021-04-21 SupplementaryMaterial/Vita.tex
Updates from Overleaf

>>>>

  \section*{Publications}
  \begin{enumerate}
    \item \textbf{Qinkun Bao}, Zihao Wang, Xiaoting Li, James Larus, and Dinghao Wu, ``Abacus: Precise Side-Channel Analysis'', In \emph{Proceedings of the 43rd International Conference on Software Engineering (ICSE 2021)}. (Technical Track)
    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Abacus: A Tool for Precise Side-Channel Analysis", In \emph{Proceedings of the 43rd International Conference on Software Engineering: Companion (ICSE-Companion 2021)}. (Artifact)

    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Quincunx: Measuring Side-channel Vulnerabilities
    By Fuzzing and Memory Auditing'', under review.

    \item \textbf{Qinkun Bao}, Zihao Wang, Quan Li, and Dinghao Wu, ``Fast Semantic-aware Function Recognition in Obfuscated Binaries'', under review.

    \item Shixiong Jing, \textbf{Qinkun Bao}, Pei Wang, Xulong Tang, and Dinghao Wu, ``Characterizing AI Model Inference Applications Running in SGX Environment'', under review.

    \item Yufei Jiang, \textbf{Qinkun Bao}, Xiao Liu, and Dinghao Wu, ``RedDroid: Android Application Redundacy Customization based on Static Analysis'', in \emph{Proceedings of the 29th IEEE International Symposium on Software Reliability Engineering (ISSRE 2018)}, Memphis, TN, October 15-18, 2018

\item Pei Wang, \textbf{Qinkun Bao}, Li Wang, Shuai Wang, Zhaofeng Chen, Tao Wei, and Dinghao Wu, ``Software Protection On-The-Go: An Empirical Study on Mobile App Obfuscation'', in \emph{Proceedings of 40th International Conference on Software Engineering (ICSE 2018)}, Gothenburg, Sweden, May 27-June 3, 2018

\item Shengru Li, Kai Han, Nirwan Ansari, \textbf{Qinkun Bao}, Daoyun Hu, Junjie Liu, Shui Yu, and Zuqing Zhu, ``Improving SDN Scalability with Protocol-Oblivious Source Routing: A System-Level Study'', \emph{IEEE Transactions on Network and Service Management}, vol. 15, no. 1, pp. 275-288, March 2018

\item Shuai Wang, Wenhao Wang, \textbf{Qinkun Bao}, Pei Wang, Xiaofeng Wang, and Dinghao Wu, ``Binary Code Retrofitting and Hardening Using SGX'', in \emph{Proceedings of the 2017 workshop on Forming an Ecosystem Around Software Transformation (FEAST17)}, co-located with CCS 2017, Dallas, USA, November 3, 2017
\end{enumerate}
